### 2019-01-22 journal/experiments.tex
move figure
more progress

Discussion with the MUSE/MUSEUM authors confirms  that adding information for passing tests, while costly, would likely improve the MUSE and MUSEUM results, given the weakness of our oracles, particularly for SpiderMonkey, and should be considered essential for ideal application of their approach.  Because the cost of recording the full mutant analysis matrix for all passing tests (rather than considering a mutant killed as soon as one test fails, as we do) is very high, and we would like to produce a comparison over a fixed computational cost, we give results for MUSE/MUSEUM over failing tests only, cautioning that we are not sure what the impact of this choice is on faults that were not localized.  For similar reasons of keeping costs low, we also used the mutation operators of Andrews vs. the more extensive Proteum \cite{Proteum} operators used in MUSE/MUSEUM's evaluations.  \comment{Even with these restrictions, running all mutants on passing tests until at least a single kill was observed took about 3 times as long as the search for repairs, which we already consider a potentially problematic cost.}  In Section \ref{sec:otherfaults} we provide some comparisons with MUSEUM and MUSE fault localization in the context of a full mutation result matrix using their preferred set of operators.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}                                                %
{\scriptsize                                                  %
\begin{code}                                                  %
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
...                                                           %
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
<         \} else \{                                          %
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
<         \}                                                  %
...                                                           %
<                   a->avail = (jsuword)sp;                   %
<               \}                                            %
...                                                           %
---                                                           %
>         RESTORE\_SP(fp);                                    %
...                                                           %
{\bf Mutant information:}                                     %
Failure repaired by 148 mutants.                              %
...                                                           %
\#3: delete statement mutant of jsinterp.c:944:               %
                                                              %
            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
        \} else \{                                            %
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
        \}                                                    %

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */                                                            %
\end{code}                                                    %
}                                                             %
\caption{Patch and explanation for fault 115}                 %
%\vspace{-0.18in}                                             %
\label{fig:explain}                                           %
\end{figure}                                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}                                                %
{\scriptsize                                                  %
\begin{code}                                                  %
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
...                                                           %
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
<         \} else \{                                          %
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
<         \}                                                  %
...                                                           %
<                   a->avail = (jsuword)sp;                   %
<               \}                                            %
...                                                           %
---                                                           %
>         RESTORE\_SP(fp);                                    %
...                                                           %
{\bf Mutant information:}                                     %
Failure repaired by 148 mutants.                              %
...                                                           %
\#3: delete statement mutant of jsinterp.c:944:               %
                                                              %
            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
        \} else \{                                            %
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
        \}                                                    %

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */                                                            %
\end{code}                                                    %
}                                                             %
\caption{Patch and explanation for fault 115}                 %
%\vspace{-0.18in}                                             %
\label{fig:explain}                                           %
\end{figure}                                                  %

@@

@@

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users simply do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique, since trying multiple metrics is impractical: a user has to examine each curve.  \comment{It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.}  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work; our improvements over any single ``reasonable'' method applied to both problems would be considerably larger (for instance, using the most obvious basis, line coverage, we see more than 17\% improvement).  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD from best-previous method is around 3\%, and statistically significant.

@@

\comment{
 Why does {\bf Repair} perform best in this setting?  It is impossible to be sure, but one  possibility is power to distinguish repairs.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.  We applied our repair localization to the MUSEUM data set, using the full Proteum mutant set and added MUSEUM-specific mutants, and for all but one of the 8 bugs in the data set, our results were equivalent to those for MUSEUM (in one case our approach fails to produce a localization).}

@@

\comment{
Finally, in contrast to many previously reported results in fault localization, typically over much simpler programs and faults than subtle compiler semantics bugs, all methods frequently failed to provide a useful localization at all.  This is presumably due to the difficulty of compiler bugs:  our approach, and MUSEUM, performed very well on complex multi-lingual faults in the MUSEUM data set.
}
\comment{ In one sense, {\bf Coverage} is the most intriguing method presented here.  While it did not perform nearly as well as {\bf Repair}, it did manage, in many cases, to rank \emph{some} faulty line highly relative to the extremely large number of statements executed in each failing GCC run (on the order of 50K-100K+ statements).  In future work, we plan to experiment with different methods for weighting frequency of coverage, perhaps using methods from machine learning, or of pruning changed coverage that is not likely to be relevant.  For example, perhaps the {\bf Repair} approach can be applied, and coverage changes present in very distant failures can be removed, though the argument is less clear, since a coverage change isn't directly associated with the onion-ring structure, and does not directly repair a set of failures.  There is much to be done if automated debugging is ever to make the lives of compiler developers easier in most cases \cite{AutoHelp}.  }

@@

The compiler experiments required a large computational budget.  However, our approach is, by design, cheaper than MUSE or Metallaxis-FL, in that, for a program with up-to-date mutation testing results (just knowing which mutants are killed, not a full matrix), it only requires executing mutants over failing tests.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average; moreover, executions can be done in parallel, most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures, and can be spread over many machines.  \comment{The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.  }

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply.   Whether sampling mutants \cite{RahulISSRE} is applicable is less clear.  Even if the FPF curve remains the same, a critical mutant for localization might be omitted.  We performed some limited experiments, and found that for a few sample sizes ranging from 13\% of mutants to 50\% of mutants or using only some mutation operators (with the exception of operator-replacement-only), APFD was always better than benchmark set's best metric.   However, the improvement in some cases was \emph{much} smaller than for the full set, and varied considerably (in some cases it was up to 2\% better than our full results).  Fault localization results were much worse, however (with relative rankings preserved) for both our techniques and MUSE/MUSEUM.  \comment{Finally, guided sampling may provide good fuzzer taming (if not fault localization):  compute vectors over a small constant-sized \cite{RahulISSRE} sample of mutants, then report highly distinct failing tests.  Other metrics, such as coverage-based comparisons, could provide hints as to likely distinct tests (and thus mutants covered by them) to focus on first.  These are likely to be different faults.  After repairing some of these, choose mutants to evaluate that are covered by multiple tests with few or no repairing mutants (since such tests are the ones most likely to be distinct but not yet identified).  Such an approach could be quite cost-effective, requiring only a relatively small number of mutant evaluations before providing useful results.}

@@

@@

The largest threat to validity is that this paper's conclusions rely on only two data sets for compilers, and a small number of non-compiler faults.  The compiler ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.

>>>>

Discussion with the MUSE/MUSEUM authors confirms  that adding information for passing tests, while costly, would likely improve the MUSE and MUSEUM results, given the weakness of our oracles, particularly for SpiderMonkey, and should be considered essential for ideal application of their approach.  Because the cost of recording the full mutant analysis matrix for all passing tests (rather than considering a mutant killed as soon as one test fails, as we do) is very high, and we would like to produce a comparison over a fixed computational cost, we give results for MUSE/MUSEUM over failing tests only, cautioning that we are not sure what the impact of this choice is on faults that were not localized.  For similar reasons of keeping costs low, we also used the mutation operators of Andrews vs. the more extensive Proteum \cite{Proteum} operators used in MUSE/MUSEUM's evaluations.  Even with these restrictions, running all mutants on passing tests until at least a single kill was observed took about 3 times as long as the search for repairs, which we already consider a potentially problematic cost.  In Section \ref{sec:otherfaults} we provide some comparisons with MUSEUM and MUSE fault localization in the context of a full mutation result matrix using their preferred set of operators.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}                                                
{\scriptsize                                                  
\begin{code}                                                  
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} 
...                                                           
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               
<         \} else \{                                          
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    
<         \}                                                  
...                                                           
<                   a->avail = (jsuword)sp;                   
<               \}                                            
...                                                           
---                                                           
>         RESTORE\_SP(fp);                                    
...                                                           
{\bf Mutant information:}                                     
Failure repaired by 148 mutants.                              
...                                                           
\#3: delete statement mutant of jsinterp.c:944:

            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 
        \} else \{                                            
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    
        \}

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */                                                            
\end{code}                                                    
}                                                             
\caption{Patch and explanation for fault 115}                 
%\vspace{-0.18in}                                             
\label{fig:explain}                                           
\end{figure}

@@

\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c|c||c||c|c|}
\hline
\multicolumn{3}{|c|}{SpiderMonkey}&\multicolumn{3}{|c|}{GCC}\\
\hline
ID & Coverage & Repair & ID & Coverage & Repair\\
\hline
1 & 2,255 & - & 1 & 44,561 & -\\
2 & 720 & - & 2 & 75 & 1\\
3 & 190 & 1 & 3 & - & -\\
4 &  - & - & 4 & 3,067 & -\\
5 & 18 & 19 & 5 & 186 & - \\
6 & 46 & 28 & 6 & 490 & - \\
7 & - & - & 7 & - & -\\
8 & 6 & 3 & 8 &260 & 4\\
   &    &    & 9 & 465 & - \\
   &    &    & 10 & 19 & - \\
   &    &    & 11 & 43,903 & 10 \\
   &    &    & 12 & 85 & 1 \\
   &    &    & 13 & 2 & - \\
   &    &    & 14 & 302 & 34 \\
   &    &    & 15 & 223 & 5 \\
   &    &    & 16 & 639 & - \\
\hline
\end{tabular}
}
\caption{Coverage localization results}
%\vspace{-0.2in}
\label{covtable}
\end{table}

Table \ref{covtable} compares the {\bf Coverage} localization with the {\bf Repair} localization.  In general, obviously, {\bf Coverage} is not as effective as {\bf Repair}.  In fact, in cases where both methods provide any localization information, there is only one instance where {\bf Coverage} is better than {\bf Repair}.  On the other hand, {\bf Coverage} provides a localization for 10 faults where {\bf Repair} offers no assistance.  The rankings for these suggestions are often poor (indeed, in some GCC cases, they are almost ludicrously bad).  However, for GCC faults 10 and 13, {\bf Coverage} produced a useful localization when all of the other methods (including MUSE and MUSEUM) failed to localize at all.  Because compiler faults are so difficult to understand and fix, it might be useful for developers to examine the top few localizations (that differ) for multiple methods.  While MUSE and MUSEUM both generally perform better than {\bf Coverage}, they almost never provide better information than {\bf Repair}.  In every case where MUSE or MUSEUM provides a useful localization (within top-25) and performs better than {\bf Repair}, the difference in ranking between MUSE or MUSEUM and {\bf Repair} is five or fewer ranking positions.  {\bf Coverage} uses a sufficiently different approach that it offers potentially useful information, even when {\bf Repair} performs badly.

@@

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users simply do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique, since trying multiple metrics is impractical: a user has to examine each curve.  The set of metrics also included methods such as comparing output signatures that are inapplicable to differential testing for wrong-code faults, the most critical compiler application.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work; our improvements over any single ``reasonable'' method applied to both problems would be considerably larger (for instance, using the most obvious basis, line coverage, we see more than 17\% improvement).  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD from best-previous method is around 3\%, and statistically significant.

@@

%\comment{
 Why does {\bf Repair} perform best in the \emph{compiler} setting in particular?  It is impossible to be sure, but one  possibility is power to distinguish repairs.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.  Our suspicion is somewhat confirmed by the results below where we used our methods with the MUSEUM mutant result set.

Finally, in contrast to many previously reported results in fault localization (which are typically over much simpler programs and faults than subtle compiler semantics bugs) all methods we applied very frequently failed to provide a useful localization at all for our compiler faults.  This is presumably due to the sheer difficulty of compiler bugs:  our approach, and MUSEUM, performed very well on complex multi-lingual faults in the MUSEUM data set.  In one sense, {\bf Coverage} is the most intriguing method presented here.  While it did not perform nearly as well as {\bf Repair}, it did manage, in many cases, to rank \emph{some} faulty line highly, relative to the extremely large number of statements executed in each failing GCC run (on the order of 50K-100K+ statements).  In future work, we plan to experiment with different methods for weighting frequency of coverage, perhaps using methods from machine learning, or of pruning changed coverage that is not likely to be relevant.  For example, perhaps the {\bf Repair} approach can be applied, and coverage changes present in very distant failures can be removed, though the argument is less clear, since a coverage change isn't directly associated with the onion-ring structure, and does not directly repair a set of failures.  In fact, since a study of the importance of delta-debugging in localization \cite{ReduceLocalize} showed that even traditional Spectrum-Based Fault Localization can \emph{sometimes} produce good results on SpiderMonkey faults (though often performing worse than even {\bf Coverage}), we suspect that combining multiple methods, using some method to cross-assess confidence might be important for obtaining reliably good compiler bug localizations.
There is much to be done if automated debugging is ever to make the lives of compiler developers easier in most cases \cite{AutoHelp}.

@@

\comment{ In one sense, {\bf Coverage} is the most intriguing method presented here.  While it did not perform nearly as well as {\bf Repair}, it did manage, in many cases, to rank \emph{some} faulty line highly relative to the extremely large number of statements executed in each failing GCC run (on the order of 50K-100K+ statements).  In future work, we plan to experiment with different methods for weighting frequency of coverage, perhaps using methods from machine learning, or of pruning changed coverage that is not likely to be relevant.  For example, perhaps the {\bf Repair} approach can be applied, and coverage changes present in very distant failures can be removed, though the argument is less clear, since a coverage change isn't directly associated with the onion-ring structure, and does not directly repair a set of failures.  There is much to be done if automated debugging is ever to make the lives of compiler developers easier in most cases \cite{AutoHelp}.  }

@@

The compiler experiments required a large computational budget.  However, our approach is, by design, cheaper than MUSE or Metallaxis-FL, in that, for a program with up-to-date mutation testing results (just knowing which mutants are killed, not a full matrix), it only requires executing mutants over failing tests.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average; moreover, executions can be done in parallel, most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures, and can be spread over many machines.

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply, without any loss of ability to identify or localize faults.

@@

Note that the largest cost in our approach, by far, is compiling the mutants.  While running all the GCC tests on the covered, compilable, test-passing mutants takes nearly 24 days of total execution time, the process is embarrasingly parallel:  no mutant/test execution depends on any other.  On the other hand, all executions of a mutant/test pair depend on having a compiler that includes that mutant built, and compiling GCC requires more time than test executions by a large margin.

We expect that fuzzer taming will mostly be performed when someone is fuzzing a compiler either for the first time or using a new technique.  If fuzzing is performed on a well-fuzzed compiler, with only incremental changes from previous versions, there is not likely to be a significant fuzzer taming problem:  fuzzing will often only detect a small number of faults, and manual triage efforts will probably suffice.  In the case of ``new'' fuzzing efforts, however, they will usually be aimed at release versions of a compiler.  For major projects such as GCC, LLVM, or V8, producing and publishing a set of ``hot'' mutants might be one solution.  \emph{Hot} mutants are mutants that 1) compile 2) pass all current tests and 3) are not known to be equivalent mutants.  Producing such mutants should be an easily automatable task without prohibitive cost, at the level of a major open source project.  Release versions are only produced a few times a year (e.g., both GCC and LLVM had 5 releases in 2018 and 4 in 2017).  In addition to fuzzer taming, such mutants would provide a useful quick benchmark for new compiler-fuzzing techniques:  if a technique can kill mutants not detectable by the compiler's test suite, it has possibilities for bug detection as well.

\subsection{Lossy Techniques}

Mutation cost reduction techniques classified as \emph{do fewer} on the other hand involve a loss of signal, not just more efficient production of the same signal.  Figures \ref{samplejs} and \ref{samplegcc} show, respectively, the results of random sampling of mutants for SpiderMonkey and GCC, by comparing the APFD obtained on a set of 30 random samples of the chosen percentage of mutants with the APFD for the full mutant set.  Because some mutants are actually misleading with respect to distinguishing faults, sometimes sampling can improve results.  Sampling 10\% of mutants directly translates to our approach requiring about 90\% less time, or less computing power if run in parallel.

Pure random sampling is fairly effective for GCC, but more mutants are required to obtain a comparable APFD on average, for SpiderMonkey.

@@

The largest threat to validity is that this paper's core conclusions rely on only two data sets for compilers, and a small number of non-compiler faults.  The compiler ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.

### 2019-01-22 journal/introduction.tex
journal start
mutants16 paper
more progress

In a PLDI 2013 paper, Chen et al. defined the \emph{fuzzer taming problem}: ``Given a potentially large collection of test cases, each of which triggers a bug, rank them in such a way that test cases triggering distinct bugs are early in the list.'' \cite{PLDI13}.  Their proposed solution was to use the Furthest-Point-First \cite{Gonzalez} (FPF) algorithm.  An FPF ranking of test cases requires a distance metric $d$ on test cases, and ranks test cases so that dissimilar tests appear earlier.  The hypothesis of Chen et al. was that dissimilar tests, by a well-chosen metric, will also fail due to different faults.
FPF is a greedy algorithm that proceeds by repeatedly adding the item with the maximum minimum distance to all previously ranked items. Given an initial seed item $r_0$, a set
$S$ of items to rank, and a distance metric $d$, FPF computes $r_i$ as $s \in S: \forall s' \in S: min_{ j < i}(d(s,r_j)) \geq min_{j < i}(d(s',r_j))$.

@@

%\subsection{The Onion-Ring and Causality}

@@

%\subsection{Contributions}

The contributions of this paper include our ideas about how to measure distance between program executions, but more importantly some practical proposals for using such a metric in compiler fuzzer taming and fault localization.  Our experimental results show that, for two realistic complex compilers, Mozilla's SpiderMonkey 1.6 JIT for JavaScript and GCC 4.3.0, using mutant response metrics improves FPF-based fuzzer taming over best previous results \cite{PLDI13}, in multiple ways.  Our fault localization approach also compares favorably to state-of-the-art fault localization techniques \cite{MUSE,multilingual,Metallaxis}, albeit with a more limited applicability (but also a lower cost).

>>>>

Chen et al. defined the \emph{fuzzer taming problem}: ``Given a potentially large collection of test cases, each of which triggers a bug, rank them in such a way that test cases triggering distinct bugs are early in the list.'' \cite{PLDI13}.  Their proposed solution was to use the Furthest-Point-First \cite{Gonzalez} (FPF) algorithm.  An FPF ranking of test cases requires a distance metric $d$ on test cases, and ranks test cases so that dissimilar tests appear earlier.  The hypothesis of Chen et al. was that dissimilar tests, by a well-chosen metric, will also fail due to different faults.
FPF is a greedy algorithm that proceeds by repeatedly adding the item with the maximum minimum distance to all previously ranked items. Given an initial seed item $r_0$, a set
$S$ of items to rank, and a distance metric $d$, FPF computes $r_i$ as $s \in S: \forall s' \in S: min_{ j < i}(d(s,r_j)) \geq min_{j < i}(d(s',r_j))$.

@@

\subsection{The Onion-Ring and Causality}

@@

\subsection{Contributions}

This paper extends our 2018 ISSRE paper \cite{ISSRE18Mutants} introducing our approach. That work, and this, suggested a novel way of measuring distance between program executions, but more importantly provided some practical proposals for using such a metric in compiler fuzzer taming and fault localization.  Our experimental results show that, for two realistic complex compilers, Mozilla's SpiderMonkey 1.6 JIT for JavaScript and GCC 4.3.0, using mutant response metrics improves FPF-based fuzzer taming over best previous results \cite{PLDI13}, in multiple ways.  Our fault localization approach also compares favorably to state-of-the-art fault localization techniques \cite{MUSE,multilingual,Metallaxis}, albeit with a more limited applicability (but also a lower cost).  We extend the earlier paper by:

\begin{itemize}
\item providing an extended example to help readers understand the metric, FPF method, and fault localization approach,
\item introducing and evaluating another compiler fault localization approach, based on code coverage changes,
\item and including experimental results summarizing the effectiveness and cost reduction provided by various optimizations of our approach.
\end{itemize}

### 2019-01-22 journal/relatedwork.tex
more progress

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines. \comment{, and is perhaps most similar to ours in assumptions, in particular ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  While we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults.} Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  \comment{MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure. }

@@

\comment{
Some approaches to localization or patching assume the possibility of a mutant/change \emph{actually} fixing a fault.  In our experiments, we found this to be highly unlikely -- most of our patches were far larger than the largest higher-order-mutants \cite{jia2009higher} anyone usually considers applying, and none were equivalent to a repair.  Previous work has shown that, across a large body of open source programs in many languages, most fault fixes were larger in size than even low-order higher-order mutants \cite{GopinathMutants}.
We speculate that fixes for compilers may be likely to be even more complex than the average, given that compilers are particularly complex software systems.  
Our primary assumption is simply that similar executions respond similarly to mutants, and in particular executions due to the same fault can be ``repaired'' by similar program changes.  These changes are likely to be \emph{related} in some causal way to the actual fault, but are unlikely to be the actual fault, for reasons of comparative complexity of mutants and real fixes.}

>>>>

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines, and is perhaps most similar to ours in assumptions. In particular we agree with ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  However, while we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults. Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure.

@@

Some approaches to localization or patching assume the possibility of a mutant/change \emph{actually} fixing a fault.  In our experiments, we found this to be highly unlikely -- most of our compiler patches were far larger than the largest higher-order-mutants \cite{jia2009higher} anyone usually considers applying, and \emph{none} were equivalent to a repair.  Previous work has shown that, across a large body of open source programs in many languages, most fault fixes were larger in size than even low-order higher-order mutants \cite{GopinathMutants}.
We speculate that fixes for compilers may be likely to be even more complex than the average, given that compilers are particularly complex software systems.  
Our primary assumption is simply that similar executions respond similarly to mutants, and in particular executions due to the same fault can be ``repaired'' by similar program changes.  These changes are likely to be \emph{related} in some causal way to the actual fault, but are unlikely to be the actual fault, for reasons of comparative complexity of mutants and real fixes.
